Home

### 2025-11-18 index.qmd
added year to copss lecture

A member of both the National Academy of Sciences and the American Academy of
Arts and Sciences, she has delivered major invited lectures, including the 2019
Breiman Lecture at NeurIPS, 2023 IMS Wald Lecture, and the COPSS DAAL Lecture
(formerly Fisher Lecture). Her group’s PCS framework (predictability,
computability, and stability) for veridical data science has become an
influential guide for transparent, trustworthy data science and AI.

>>>>

A member of both the National Academy of Sciences and the American Academy of
Arts and Sciences, she has delivered major invited lectures, including the 2019
Breiman Lecture at NeurIPS, 2023 IMS Wald Lecture, and the 2023 COPSS DAAL
Lecture (formerly Fisher Lecture). Her group’s PCS framework (predictability,
computability, and stability) for veridical data science has become an
influential guide for transparent, trustworthy data science and AI.
